APOGEE CATALOG OF 10,000+ M DWARFS MEASURED BY DATA-DRIVEN MODELS

### 2018-07-23 paper/draft1/draft1.tex
update figures

While The Cannon can in principle be trained on any physical or empirical labels.

@@

For each training sample

Two tests of consistency were used to assess the validity of our derived test labels (Figure \ref{fig:west_validation}). The self-test comparing training labels and test labels where precision and bias of the model are calculated as the standard deviation and mean of the difference in training and test labels respectively.

@@

We note for this model XX out of 87 sources show strong rotational line broadening (as indicated by the red circles in Figure \ref{fig:mann_validation}), however the model

\subsection{Test Sample}

@@

\begin{figure}[ht]
\begin{center}
\includegraphics[width=18cm]{figures/self_and_validation_test_spt_snr.png}
\end{center}
\caption{Consistency test for the West-trained spectral type model; self-test \textit{(left)}, and leave-one-out cross validation \textit{(right)}.} \label{fig:west_validation}
\end{figure}

\begin{figure}[ht]
\begin{center}
\includegraphics[width=18cm]{figures/self_and_validation_test_teff_snr.png}
\includegraphics[width=18cm]{figures/self_and_validation_test_fe_h_snr.png}
\end{center}
\caption{Consistency test for the Mann-trained temperature/metallicity type model; self-test \textit{(left)}, and leave-one-out cross validation \textit{(right)}.} \label{fig:mann_validation}
\end{figure}

%---------------------------
\begin{figure}[ht]
\plotone{figures/Spectral_Sequence_1.pdf}
\plotone{figures/Spectral_Sequence_2.pdf}
\plotone{figures/Spectral_Sequence_3.pdf}
\caption{ Spectral sequence of dwarfs in training set M0-M9; separate plots show three detector chips of APOGEE spectrum (black), the best fit Cannon trained model (red) with highlighted spectral type sensitive regions identified in \citealt{Desphande:2013}.} \label{fig:sp_sequence}
\end{figure}

@@

%---------------------------
\begin{figure}[!htb]
\minipage{0.32\textwidth}
  \includegraphics[width=\linewidth]{figures/test_cmd_teff.png}
\endminipage\hfill
\minipage{0.32\textwidth}
  \includegraphics[width=\linewidth]{figures/test_cmd_feh.png}
\endminipage\hfill
\minipage{0.32\textwidth}%
  \includegraphics[width=\linewidth]{figures/test_cmd_chisq.png}
\endminipage
\end{figure}

>>>>

The Cannon model can in principle be trained on any physical or empirical labels available. However, limitations to consider are that test labels from The Cannon are only accurate if the training labels accurate, and only precise if the training labels are measured using a consistent method. The Cannon does not extrapolate well outside the parameter space of the training sample.

@@

For each model, two tests of consistency were used to assess the validity of our derived test labels. The self-test comparing training labels and test labels where precision and bias of the model are calculated as the standard deviation and mean of the difference in training and test labels respectively.

@@

We note for this model 6 out of 87 sources show strong visible rotational line broadening (as indicated by the red circles in Figure \ref{fig:mann_validation}), however the model

\color{gcolor}{HOGG: Some commentary on why $\chi^2$ is higher than expected.}\color{black}

\subsection{Test Sample}
Some validation of our test label results...

@@

\begin{figure}[ht]
\begin{center}
\includegraphics[width=15cm]{figures/self_and_validation_test_spt_snr.png}
\end{center}
\caption{Consistency test for the West-trained spectral type model; self-test \textit{(left)}, and leave-one-out cross validation \textit{(right)}.} \label{fig:west_validation}
\end{figure}

\begin{figure}[ht]
\begin{center}
\includegraphics[width=15cm]{figures/self_and_validation_test_teff_snr.png}
\includegraphics[width=15cm]{figures/self_and_validation_test_feh_snr.png}
\end{center}
\caption{Consistency test for the Mann-trained temperature/metallicity type model; self-test \textit{(left)}, and leave-one-out cross validation \textit{(right)}. Sources with strong rotational broadening (2M07171706−0501031, 2M08155393+3136392, 2M09174473+4612246, 2M10331367+3409120, 2M15594729+4403595, 2M13400879+4346380) are identified with red circles.} \label{fig:mann_validation}
\end{figure}

%---------------------------
\begin{figure}[ht]
\plotone{figures/Spectral_Sequence_1.pdf}
\plotone{figures/Spectral_Sequence_2.pdf}
\plotone{figures/Spectral_Sequence_3.pdf}
\caption{Spectral sequence of dwarfs in training set M0-M9; separate plots show three detector chips of APOGEE spectrum (black), the best fit Cannon trained model (red) with highlighted spectral type sensitive regions identified in \citealt{Desphande:2013}.} \label{fig:sp_sequence}
\end{figure}

@@

%---------------------------
\begin{figure}[ht]
\plottwo{figures/test_cmd_chisq.png}{figures/test_fit_distribution.png}
\caption{The distribution of $\chi^2$ fits for all 14,827 sources in the APOGEE-Gaia cross match, with color cuts $1<G_{BP}-G_{RP}<6$ and $7.5<M_{G}<20$ and $\pi>0$. Note that there are $>$1,000 sources above the main sequence, many of which are pre-main sequence stars and main sequence binaries.}
\plottwo{figures/test_cmd_teff.png}{figures/test_cmd_feh.png}
\caption{Gaia color-magnitude diagram of 13,915 sources, selected with $\chi^2<200,000$ out of the total test sample.}
\end{figure}
